%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{John Gordon}{Last updated \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:john.gordon@gordonjl.com}{john.gordon\mbox{}@\mbox{}gordonjl.com}\sbull
\textsmaller{207.329.4111}\sbull
\href{https://www.linkedin.com/in/gordonjl/}{www.linkedin.com/in/gordonjl/}
\\
86 Edwards Street\sbull
Portland, Maine\sbull
USA

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Experienced software engineering manager, with both hard 
and soft skills.}
\\
\\
Moving to San Francisco in the '90s during the dotcom boom, I became a coder on a 40-developer, remotely-distributed team, developing large features for a major retail banking website. After becoming a skilled tech lead, I moved into management in 2013, combining my communication skills with my technical abilities to grow my own team of software developers from eight to eighteen individuals. I am an experienced manager, specializing in managing remote teams, and am a highly-skilled software consultant, collaborating with clients to develop large, enterprise-level projects.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.portlandwebworks.com}{Portland Webworks}}
  {\textsc{Portland, Maine}} {%
  \headedsubsection
    {Director of Software Development}
    {2013 -- present}
    {\bodytext{Portland Webworks is a software consulting company, specialized in creating web-based, data-driven applications.  I report directly to the company owner. In charge of a team of 18 developers, I am responsible for managing the team, introducing and maintaining project process, supporting the Business Development unit as technical consultant, and coordinating with clients and other departments within the company.

    \begin{itemize}
      \item Grew the software development team from 8 to 18 developers, member tenure averaging 4 years.
      \item Replaced Waterfall process with Scrum and Kanban methodologies.
      \item Advanced the team's careers, assigning members to developer and techincal lead roles, and providing feedback in 1:1 sessions.
      \item Increased accountability by gathering team and company metrics and displaying on monitors in the office.
      \item Freed up resources and kept team morale high by personally maintaining legacy projects (JSF, Struts, ExtJS, DB2).
      \item Increased team productivity by standardizing processes and tools across projects, reducing ramp-up time for new team members.
      \item Introduced hiring remote developers, now a third of the team, making it possible to staff our increasing number of projects.
    \end{itemize}}}
  \headedsubsection
    {Senior Software Developer}
    {2010 -- 2013}
    {\bodytext{Technical lead on projects key to the company's success
    \begin{itemize}
      \item Developed custom word processor tool that tightly integrated with Maine's Judicial systems, allowing for auto-insertion of court case information into legal documents.
      \item Perform B/A and project technical Discovery, formed teams, and gave direction with both in-house and remote European-based teams.
      \item Created a Single Page Application, with offline capabilities, to track fisherman's seafood catch
      \item Developed online Medicaid renewal application system for Idaho's Departement of Health and Welfare
      \item Led the adoption of Google Apps and Bitbucket 
    \end{itemize}
    }
    \vspace{0.5em}
    {\bodytext{
    \emph{Technologies}
    \\
    Java\sbull Spring and Spring Boot\sbull Hibernate\sbull AngularJS 1.x\sbull Angular 2+\sbull Cocoa\sbull Objective-C\sbull Oracle\sbull MySql\sbull Postgresql\sbull ExtJS\sbull Clover ETL\sbull Groovy\sbull Grails\sbull Ruby on Rails\sbull Selenium
    }}
  }  
   
}



\headedsection
  {\href{https://www.idexx.com/en/}{IDEXX}}
  {\textsc{Westbrook, Maine}} {

  \headedsubsection
    {Technical Lead}
    {Feb 2009 -- March 2010}
    {\bodytext{IDEXX is an American multinational corporation engaged in the development, manufacture, and distribution of products and services for the companion animal veterinary, livestock and poultry, water testing, and dairy markets. I joined to lead the development of a Laboratory Information Management System. The team included five developers, two QA, and other support staff. After one year of development, the project was delivered on time and deployed to all of IDEXX's global laboratories. The system handled every facet of laboratory activity, from requisition and sample intake processing, testing (both via manual entry and insturment interface), analysis, reporting, and billing. The application is based on SOA architecture, utilizing Oracle’s Service Bus, Weblogic Integration platform, and Data Services Integration backend.
    \begin{itemize}
      \item Worked closely with the project manager and business analyst team to identify work load for all sprints, delegating work to individual developers.
      \item Actively develop web services and Swing code in addition to leading the team.
      \item Responsible for change control, branching, and merging of the code base.
      \item Created automated, one-click, build-and-deployment process for publishing Webstart Swing client application to the various environments.
      \item introduced Atlassian Fisheye/Crucible, Hudson and Jabber Chatroom to the department, all geared towards improving the continuous integration feedback loop.
      \item General management tasks for direct reports; performance reviews, one-to-ones. Led daily status meeting; 15 attendees.
    \end{itemize}
    }}
    \vspace{0.5em}
    {\bodytext{
    \emph{Technologies}
    \\
    Spring AOP\sbull XDoclet\sbull Oracle ODSI\sbull Oracel OSB\sbull Ora- cle WLI\sbull Axis Web services\sbull Watir\sbull nUnit\sbull jUnit\sbull jMock\sbull Ant\sbull NAnt\sbull UML, Weblogic 10/11g\sbull Java Swing\sbull Javascript
    }}

    }


\headedsection
  {\href{https://en.wikipedia.org/wiki/Washington_Mutual}{Washington Mutual Bank (\acr{WAMU})}}
  {\textsc{Emeryville, California}}
  {
  \headedsubsection
    {Senior Software Developer}
    {2002 -- 2007}
    {\bodytext
      {
        Washington Mutual Bank was the largest US savings and loan. I worked on many projects, but my most significant work was developing and maintaining the mortgage product-pricing web service and working on an Agile team tasked with developing new industry functionality that for the first time enabled customers to open bank accounts totally online.
        \begin{itemize}
          \item Enabled funding of new online account originations via debit/credit card.
          \item Implemented one-step account origination form for eligible customers. Form wrapped existing wizard-based application process to present a single form for users to complete.
          \item Completed a major refactoring of Wamu’s account originations funding process.
          \item Modularized each funding option to enable easy addition of future funding options.
          \item Implemented automated build process for wamu.com, dramatically cutting down build time and greatly increasing overall stability of the code base.
          \item Designed and implemented back end processes for online overdraft notification to process high traffic levels.
          \item Created J2ee Axis Web Service to wrap legacy systems for use in modern, front-end application, decoupling the web app from legacy system and greatly speeding development.
          \item Created ASP.Net longbeachmortgage.com broker web site to display loan pro-cessing status. Site implemented using Web Service SOA strategy.
          \item Created and maintained a high-traffic .Net Web Service and accompanying man- agement/testing J2ee web application, responsible for providing mortgage pricing data for multiple applications.
          \item Created internal incentives and promotions ASP.Net web application for sales
          \item team. Heavy emphasis on de-coupling the view enabled quarterly re-design of the site without changes to the underlying business logic.
        \end{itemize}
      }

    }
  }

\vspace{1em}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Software design and implementation, with(in) a team.  Big fan of Agile methodologies (Scrum and Kanban), automated deployment (Capistrano) and continuous integration (Hudson/Jenkins).  Enjoys writing Ruby/\nsp Python/\nsp Java/\nsp \CPP, yet flirts regularly with Haskell.  Solid knowledge of web technologies:\ \acr{HTML+CSS}, \acr{XML}, \acr{RDF}, \acr{REST}, \acr{SOAP} and JavaScript (mostly Angular and jQuery).  Linux administration skills:\ Bash, Apache, My\acr{SQL}, Postgres\acr{SQL}, virtualization/cloud (Vagrant, Open\acr{VZ}, \acr{VM}ware, \acr{KVM}, Xen and \acr{EC}2), datacenter automation (Puppet and Chef).}


\spacedhrule{2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.eur.nl/english}{The George Washington University}}
  {\textsc{Washington, D.C.}} {%
  \headedsubsection
    {Liberal Arts Major}
    {1993 -- 1995}
    {}
}

\headedsection
  {\href{http://www.libanonlyceum.nl}{Montgomery Community Colleg}}
  {\textsc{Rockville, Maryland}} {%
  \headedsubsection
    {Associates Degree}
    {1991 -- 1993} {}
}

\vspace{0.5em}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {alternative transportation, chess, parenting, poker, software engineering (methodologies), squash, travel}


\end{document}
